\section{Methods}
\label{sec:methods}

The goal of our method is to generate a segmentation mask for an object of interest in each frame of a single image volume or video sequence using only point-wise annotations and without knowing the image type or object of interest beforehand.

To do so, we propose a novel approach within the Positive-Unlabeled learning setting, that learns the segmentation of the object identified by the point-wise annotations. Our method makes use of a non-negative risk estimator~\cite{kiryo17}, which heavily relies on knowing the proportion of positive samples in the data. While unavailable in our setting, we introduce a novel self-supervised method to estimate this key value via an iterative learning procedure within a Bayesian estimation framework. We then devise a stopping condition to halt training at an appropriate point. Last, a spatio-temporal tracking framework is applied to regularize the output of our approach over the complete volume information.

We describe our approach now in more detail. In the following subsection, we introduce the Positive-Unlabeled learning framework and its non-negative risk estimator. We then describe in 
Sec.~\ref{sec:pi_estim} our self-supervised approach to learn effective class priors. Last, we detail how we leverage the spatio-temporal regularizer, and provide our implementation details
in Sec.~\ref{sec:tracking} and Sec.~\ref{sec:implementation}, respectively.
\input{chapters/nnpu/method_nnpu.tex}
\input{chapters/nnpu/method_bayesian.tex}
\input{chapters/nnpu/method_tracking.tex}
\input{chapters/nnpu/method_train_details.tex}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
