\resetfigpath{dec}

\chapter{A Deep Embedded Clustering approach}
This chapter presents an approach whose ambition is to improve on two components of the previous chapter, namely
(1) The pairwise similarity model that intervenes in the frame-to-frame likelihood model, and
(2) The feature extraction method that intervenes in the foreground prediction model.
In particular, we aimed at generating pairwise similarity labels that would serve to train a pairwise similarity metric, as can be found, for example, in the deep siamese network for multiple object tracking of \cite{cuan18}, or the deep cosine metric learning of \cite{wojke18}.
In our scenario, pairwise similarity labels are not available, which therefore justifies a preliminary self-supervised approach to generate them.
This self-supervised task relies on the \gls{dec} approach, which devises a training scheme that
alternates between a cluster assignment step and centroid update step, similar in spirit to the K-mean algorithm, while the features corresponding to these samples are obtained from the bottleneck of a \gls{cnn} and optimized jointly with the clustering objective.

As will be shown in our experiments, this approach proved to be ineffective in practice, as the above task is very hard to achieve.
In particular, we observed a high sensitivity to a number of hyper-parameters that made the learning process unstable.
The learning rate, the update period of centroids, and the initial values of clusters were tightly dependent, often bringing the learning process to a degenerate solution.
Next, assuming that the above went smoothly, our pairwise similarity module would often bring negligible improvements.
Concretely, several strategies were implemented, namely a siamese network, a cosine similarity metric learning, and a \gls{gmm}.
Neither provided significant improvements to our baseline models.
We therefore chose to present results using the simpler \gls{gmm}.

Despite these negative results, we chose to provide here our general approach for future reference.

\input{chapters/dec/02_intro}
\input{chapters/dec/03_methods}
\input{chapters/dec/04_experiments}
\input{chapters/dec/05_conclusion}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../main"
%%% End:
